---
title: "Zias_data"
author: "Jaylen Johnson"
date: "2023-04-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file="Zias_data.csv")
mydata$Scorpion_ID <- as.factor(mydata$Scorpion_ID)
```

#   Analysis of NumProbes

```{r}
boxplot(NumProbes~Scorpion_ID,data=mydata)
```


This plot shows that when the scorpions were at higher temperatures they were more likely to sting than those who were kept at lower temperatures.

```{r}
favstats(NumProbes~Scorpion_ID,data=mydata)
```


The average amount of probes for scorpions placed in high temperatures was 6.5 which is much lower than that of the 23.5 of those placed in lower temperatures.  


```{r}
t.test(NumProbes~Scorpion_ID,data=mydata)
```
  
This data at the 95% confidence level has some difference between scorpions that are proved at low and high temperatures. 

#   Analysis of TimeSting

```{r}
boxplot(TimeSting~Scorpion_ID,data=mydata)
```

This plot shows that it took Scorpions at lower temperatures longer to sting than that of scorpions at higher temperatures.

```{r}
favstats(TimeSting~Scorpion_ID,data=mydata)
```


Scorpions placed in higher temperatures on average took 3 times less time to sting than that of the scorpions in lower temperatures.

```{r}
t.test(TimeSting~Scorpion_ID,data=mydata,conf.level=.9)
```

At the 90% confidence level it can be concluded that there is a difference between scorpions placed in lower or higher temperatures.  At confidence levels 95% and 99% there is no discernible difference between the scorpions.











